Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-02-03 ms.tex
small wording changes throughout

	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector

@@

	This noise would  only become relevant when attempting to observe integrations of 1 group up the ramp.

@@

\begin{deluxetable*}{ccCrlcc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{Test Year} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} &
\colhead{Flight Hardware?} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY)} &
\colhead{(ppm)} &
\colhead{} &
\colhead{} &
\colhead{}
}
\startdata
Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging & N\\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

@@

\clearpage
\subsubsection{Dark Baseline Test}\label{sec:darkBaseline}
In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
While 1/f is highly correlated within an aperture and results in a large value.

@@

\begin{itemize}
	\item \textbf{1/f Noise:} This is a major contributor to the noise.
	It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
	Fortunately, 1/f noise appears to average like $1/\sqrt{N_{int}} $ from integration to integration.
	We found efficient reductions in 1/f noise by subtracting the median value from each row in each amplifier.
	This will be possible for imaging time series but not grism spectroscopy, where one must use the outer background regions in the spectral dispersion direction to reduce 1/f noise.
	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise.
	\item \textbf{Subpixel Sensitivity:} The NIRCam detectors all exhibit some degree of crosshatching patterns along crystallographic planes of HgCdTe.
	Crosshatching structures extend down to the subpixel level where they will not be corrected for in standard flat fielding procedures, especially at the wavelengths that are below Nyquist sampling ($< 3.7\mu$m for the long wavelength and ($1.8\mu$m for the short wavelength).
	The ALONG detector (used for grism time series) experiences the most pronounced crosshatching amplitudes.
	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.
	Accurate target acquisition will ensure that the same sets of pixels will be used for all grism time series, which permits detailed characterization of the subpixel behavior for re-use on multiple different visits.
	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} HST observations of exoplanets experience a well-known ``hook effect'' at the beginning of each orbit that rises like an exponential function of time.
	This is now understood as charge trapping in the detectors \citep{zhou2017chargeTrap}.
	JWST shows a much smaller ``hook effect'' and also much faster charge trap timescales, such that we expect it to be a negligible contributor so the NIRCam error budget.
	Long timescale traps contribute less then 1e-/DN/px so they are less problematic.
\end{itemize}

>>>>

	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector.
	These can be reduced with reference pixels or background subtraction.

@@

	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).

@@

\begin{deluxetable*}{ccCrlcc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{Test Year} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} &
\colhead{Flight Hardware?} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY)} &
\colhead{(ppm)} &
\colhead{} &
\colhead{} &
\colhead{}
}
\startdata
%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole \& flood-illuminated imaging & N\\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

\subsection{Differential Spectrum}
We investigate whether the lamp fluctuations can be removed by dividing by a signal-to-noise-weighted broadband time series.
\begin{figure*}
\gridline{\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_differential.pdf}{0.49\textwidth}{Differential Time series}}
\caption{Differential time series
}\label{fig:otisLWDiffdynSpec}
\end{figure*}

@@

\clearpage
\subsubsection{Dark Baseline Test}\label{sec:darkBaseline}
In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
While 1/f is highly correlated within an aperture and results in a large value of noise per integration, the integrations are all statistically independent. Threfore, on 10 minute long timescales, the total noise of the readout electronics including 1/f and dark current in the aperture drops to 10 ppm.

@@

\begin{itemize}
	\item \textbf{1/f Noise:} This is a major contributor to the noise.
	It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
	Fortunately, 1/f noise appears to average like $1/\sqrt{N_{int}} $ from integration to integration.
	We found efficient reductions in 1/f noise by subtracting the median value from each row in each amplifier.
	This will be possible for imaging time series but not grism spectroscopy, where one must use the outer background regions in the spectral dispersion direction to reduce 1/f noise.
	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise.
	\item \textbf{Subpixel Sensitivity:} The NIRCam detectors all exhibit some degree of crosshatching patterns along crystallographic planes of HgCdTe.
	Crosshatching structures extend down to the subpixel level where they will not be corrected for in standard flat fielding procedures, especially at the wavelengths that are below Nyquist sampling ($< 3.7\mu$m for the long wavelength and ($1.8\mu$m for the short wavelength).
	The ALONG detector (used for grism time series) experiences the most pronounced crosshatching amplitudes.
	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
	Fortunately, the pointing drifts are expected to be very small other than brief and infrequent High Gain Antenna moves, so the expected standard deviation of flux due to pointing jitter is only $\sim$ 6 ppm.
	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.
	Accurate target acquisition will ensure that the same sets of pixels will be used for all grism time series, which permits detailed characterization of the subpixel behavior for re-use on multiple different visits.
	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} HST observations of exoplanets experience a well-known ``hook effect'' at the beginning of each orbit that rises like an exponential function of time.
	This is now understood as charge trapping in the detectors \citep{zhou2017chargeTrap}.
	JWST shows a much smaller ``hook effect'' and also much faster charge trap timescales, such that we expect it to be a negligible contributor so the NIRCam error budget.
	Long timescale traps contribute less then 1e-/DN/px so they are less problematic.
\end{itemize}
